Hypertension and microbiome

### 2019-01-25 articletwo.Rmd
Minor

```{r session info}
sessionInfo()
```

@@

diversity <- merge(alpha.diversity, beta.diversity, by = "response") %>%
    merge(names.dset %>% select(Covariate, Category, Name), by.x ="response", by.y = "Covariate") %>%
    mutate(Qstar = ifelse(p.value < 0.05, '*', ' '))

fig.height <- 4.0 + nrow(diversity) * 0.33
fig.permar2.text <- "R2 of variable \nin Bray-Curtis distance" # TODO latexify expression?
fig.textsize <- 15
amaxb <- diversity %>% pull(estimate) %>% abs %>% max %>% signif(., digits = 2)
```

```{r alphabeta alpha}
plot.alpha.diversity <- ggplot(diversity, aes(x=reorder(Name, R2),  y = 1, fill = estimate)) +
    geom_bar(stat="identity", color="black") +
    coord_flip() +
    scale_fill_gradientn(colours = c("darkblue", "blue", "white", "red", "darkred"),
                         values = rescale(c(-amaxb,-0.1, 0, 0.1, amaxb)),
                         name = 'Regression coefficient \nin linear model \nfor Shannon index',
                         limits = c(-1.05*amaxb, 1.05*amaxb),
                         na.value = "black") +
    theme_classic(20) +
    geom_point(aes(Name, y=0.5, shape=Qstar), show.legend=TRUE, color='black', size=20) +
    scale_shape_manual(name="",
                       values=c('*'='*', ' '=' '),
                       labels=c("*"="significant at FDR 0.05", ' '=' '),
                       breaks=c("*", ' ')) +
    xlab("") +
    ylab("") +
    theme(legend.position="right",
          legend.title=element_text(size = 20),
          legend.direction="vertical",
          legend.text=element_text(size = floor(0.75*20)),
          legend.box.margin=margin(0,0,0,0,"pt"),
          legend.margin=margin(0,0,0,0,"pt"),
          legend.justification="left",
          axis.line.y = element_line(linetype="blank"),
          axis.line.x = element_line(linetype="blank"),
          legend.title.align = 0,
          legend.text.align = 0,
          axis.text.y = element_text(color="black"),
          axis.text.x = element_text(color="black"))+
    scale_y_continuous(breaks=c(0.5), labels=c(expression(alpha)))

@@

plot.gtable.alpha.diversity.stripped <- ggplot_gtable(ggplot_build(plot.alpha.diversity))
```

```{r alphabeta beta}
plot.beta.diversity <- ggplot(diversity, aes(x = reorder(Name, R2), y= R2)) +
    geom_bar(stat="identity", color='black') +
    coord_flip() +
    theme_classic(fig.textsize) +
    ylab(fig.permar2.text) +
    theme(axis.text.y = element_text(color="black"),
          axis.text.x = element_text(color="black"),
          legend.position="right",
          legend.direction="vertical",
          legend.box.margin=margin(0,0,0,0,"pt"),
          legend.margin=margin(0,0,0,0,"pt"),
          legend.justification="left",
          legend.title.align = 0,
          legend.text.align = 0)

@@

plot.beta.diversity <- plot.beta.diversity  +
    theme(axis.text.x = element_blank(),
          axis.text.y = element_blank(),
          axis.title.x  =  element_blank(),
          axis.title.y = element_blank(),
          legend.position = "none")
plot.gtable.beta.diversity.stripped <- ggplot_gtable(ggplot_build(plot.beta.diversity))
```

```{r save grob}
gs4 <- list(plot.alpha.diversity.yaxis,
            plot.gtable.alpha.diversity.stripped$grobs[[6]],
            plot.gtable.beta.diversity.stripped$grobs[[6]],
            plot.alpha.diversity.legend,
            plot.alpha.diversity.gtable$grobs[[7]],
            plot.gtable.beta.diversity$grobs[[7]],
           plot.xlab.beta.diversity)
#           plot.gtable.beta.diversity.stripped[[3]])

g4 <- arrangeGrob(grobs = gs4,
            layout_matrix = rbind(
                c(1,2,8,3,NA),
                c(1,2,8,3,4),
                c(1,2,8,3,NA),
                c(1,2,8,3,NA),
                c(NA,5,NA,6,NA),
                c(NA,NA,NA,7,NA)),
            widths=c(4,0.7,0.5,5,5),
            heights=c(3,12,8,21,1,2))

ggsave(file = "cache/alpha-beta.png", plot=g4, height=10, width=11)

>>>>

```{r Officer importer, code = sessionInfo()}
```

@@

diversity <- merge(alpha.diversity, beta.diversity, by = "response") %>%
    merge(names.dset %>% select(Covariate, Category, Name), by.x ="response", by.y = "Covariate") %>%
    mutate(Qstar = ifelse(p.value < 0.05, '*', ' '))
```

```{r alphabeta alpha}
plot.alpha <- function(diversity,  width = .4, posdodge = .25, aspectratio = 2, colorlimit = 0.25) {
    plot.alpha.diversity <- ggplot(diversity, aes(x=reorder(Name, R2),  y = 1, fill = estimate)) +
        geom_bar(stat="identity", color="black") +
        coord_flip() +
        scale_fill_gradientn(colours = c("darkblue", "blue", "white", "red", "darkred"),
                             values = rescale(c(-amaxb,-0.1, 0, 0.1, colorlimit)),
                             name = 'Regression coefficient \nin linear model \nfor Shannon index',
                             limits = c(-1.05*amaxb, 1.05*amaxb),
                             na.value = "black") +
        theme_classic(20) +
        geom_point(aes(Name, y=0.5, shape=Qstar), show.legend=TRUE, color='black', size=20) +
        scale_shape_manual(name="",
                           values=c('*'='*', ' '=' '),
                           labels=c("*"="significant at FDR 0.05", ' '=' '),
                           breaks=c("*", ' ')) +
        xlab("") +
        ylab("") +
        theme(legend.position="right",
              legend.title=element_text(size = 14),
              legend.direction="vertical",
              legend.text=element_text(size = floor(0.75*20)),
              legend.box.margin=margin(0,0,0,0,"pt"),
              legend.margin=margin(0,0,0,0,"pt"),
              legend.justification="left",
              axis.line.y = element_line(linetype="blank"),
              axis.line.x = element_line(linetype="blank"),
              legend.title.align = 0,
              legend.text.align = 0,
              axis.text.y = element_text(color="black"),
              axis.text.x = element_text(color="black"))+
        scale_y_continuous(breaks=c(0.5), labels=c(expression(alpha)))

@@

    plot.gtable.alpha.diversity.stripped <- ggplot_gtable(ggplot_build(plot.alpha.diversity))
    return(list(plot = plot.gtable.alpha.diversity.stripped$grobs[[6]],
                yaxis = plot.alpha.diversity.yaxis,
                xaxis = plot.alpha.diversity.gtable$grobs[[7]],
                legend = plot.alpha.diversity.legend))
}

```{r alphabeta beta}
plot.beta <- function(diversity, fig.permar2.text = "R2 of variable \nin Bray-Curtis distance", fig.textsize = 15) {
    plot.beta.diversity <- ggplot(diversity, aes(x = reorder(Name, R2), y= R2)) +
        geom_bar(stat="identity", color="black") +
        coord_flip() +
        theme_classic(fig.textsize) +
        ylab(fig.permar2.text) +
        theme(axis.text.y = element_text(color="black"),
              axis.text.x = element_text(color="black"),
              legend.position="right",
              legend.direction="vertical",
              legend.box.margin=margin(0,0,0,0,"pt"),
              legend.margin=margin(0,0,0,0,"pt"),
              legend.justification="left",
              legend.title.align = 0,
              legend.text.align = 0)

@@

    plot.beta.diversity <- plot.beta.diversity  +
        theme(axis.text.x = element_blank(),
              axis.text.y = element_blank(),
              axis.title.x  =  element_blank(),
              axis.title.y = element_blank(),
              legend.position = "none")
    plot.gtable.beta.diversity.stripped <- ggplot_gtable(ggplot_build(plot.beta.diversity))

      return(list(plot =plot.gtable.beta.diversity.stripped$grobs[[6]],
                xaxis = plot.gtable.beta.diversity$grobs[[7]]))
}
```

```{r save grob}
alpha.diversity <- plot.alpha(diversity)
beta.diversity <- plot.beta(diversity)
gs4 <- list(alpha.diversity$yaxis,
            alpha.diversity$plot,
            beta.diversity$plot,  
            alpha.diversity$legend,
            alpha.diversity$xaxis,
            beta.diversity$xaxis,
           plot.xlab.beta.diversity)

g4 <- arrangeGrob(grobs = gs4,
            layout_matrix = rbind(
                c(1,    2,    3, 4),
                c(NA, 5,    6, NA),
                c(NA, NA, 7, NA)),
            widths=c(4, 0.7, 5, 5),
            heights=c(10, 1, 2))
ggsave(file = "cache/alpha-beta.png", plot=g4, height=3, width=9)
```

### 2019-01-25 rrbiome.Rmd
Minor

 ```{r adonis calculation, cache = FALSE}
if (!file.exists("rds/adonis.species.rds")) {

    adonis.species <- calculateadonis(dset = meta(pseq.species),
                    matrix = bray.dist.m.species,
                        covariates = c("BL_AGE", "SEX", "BMI", "CURR_SMOKE", "Q57X", "DIAB", "BL_USE_RX_C03", "BL_USE_RX_C07", "BL_USE_RX_C08", "BL_USE_RX_C09"),
                    npermutations = 1)

    saveRDS(adonis.species, file = "rds/adonis.species.rds")

} else {
     adonis.species  <- readRDS("rds/adonis.species.rds")
}
```

>>>>

 ```{r adonis calculation, cache = FALSE}
 if (!file.exists("rds/adonis.species.rds")) {
     adonis.species = list()
     adonis.species$min <- calculateadonis(dset = meta(pseq.species),
                                           matrix = bray.dist.m.species,
                                           covariates = c("BL_AGE", "SEX"),
                                           npermutations = 99)
     adonis.species$max <- calculateadonis(dset = meta(pseq.species),
                                           matrix = bray.dist.m.species,
                                           covariates = c("BL_AGE", "SEX", "BMI", "CURR_SMOKE", "Q57X", "DIAB", "BL_USE_RX_C03", "BL_USE_RX_C07", "BL_USE_RX_C08", "BL_USE_RX_C09"),
                                           npermutations = 99)

     saveRDS(adonis.species, file = "rds/adonis.species.rds")
    } else {
     adonis.species  <- readRDS("rds/adonis.species.rds")
}
```
